---
title: "p8105_hw5_zh2494"
author: "zhuolun"
date: "11/16/2021"
output: github_document
---

```{r}
library(p8105.datasets)
library(tidyverse)
library(viridis)

knitr::opts_chunk$set(
  echo = TRUE,
  warning = FALSE,
  fig.width = 8,
  fig.height = 6,
  out.width = "90%"
)
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

theme_set(theme_minimal() + theme(legend.position = "bottom"))
```

# question 1
```{r}
homicide_df = 
  read_csv("./data/homicide-data.csv", na = c("", "Unknown")) %>% 
  mutate(city_state = str_c(city, state),
         resolution = case_when(
           disposition == "Closed without arrest" ~ "unsolved",
           disposition == "Open/No arrest"        ~ "unsolved",
           disposition == "Closed by arrest"      ~ "solved")) %>% 
  relocate(city_state) %>% 
  filter(city_state != "TulsaAL")
```

Let's focus on Baltimore, MD.
```{r}
baltimore_df = 
  homicide_df %>% 
  filter(city_state == "BaltimoreMD")

baltimore_summary = 
  baltimore_df %>% 
  summarize(
    unsolved = sum(resolution == "unsolved") ,
    n = n()
  )
baltimore_test =
  prop.test(
  x = baltimore_summary %>% pull(unsolved), 
  n = baltimore_summary %>% pull(n))

baltimore_test %>% 
  broom::tidy()
```
there is 0.6455 that unsolved homicide in Baltimore unsolved
The CI is from 0.628 to 0.663

iterate across cities, test it on each cites.
```{r}
prop_test_function = function(city_df){
  city_summary = 
    city_df %>% 
    summarize(
      unsolved = sum(resolution == "unsolved") ,
      n = n()
    )
  
  city_test =
    prop.test(
    x = city_summary %>% pull(unsolved), 
    n = city_summary %>% pull(n))

  return(city_test)
}

# prop_test_function(baltimore_df)

#homicide_df %>% 
#  filter(city_state == "AlbuquerqueNM") %>% 
#  prop_test_function()
```

iterate across all cites
```{r}
results_df = 
  nested_df = 
  homicide_df %>%
  nest(data = uid:resolution) %>% 
  mutate(
    test_results = map(data, prop_test_function),
    tidy_results = map(test_results, broom::tidy)
  ) %>% 
  select(city_state, tidy_results) %>% 
  unnest(tidy_results) %>% 
  select(city_state, estimate, starts_with("conf"))
```

try to make a plot showing estimates and confidence intervals

```{r}
results_df %>% 
  mutate(city_state = fct_reorder(city_state, estimate)) %>% 
  ggplot(aes(x = city_state, y = estimate)) + 
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
```

```{r}
homicide_df %>% 
  group_by(city_state) %>% 
  summarize(
    unsolved = sum(resolution == "unsolved"),
    n = n()
  ) %>% 
  mutate(
    test_results = map2(unsolved, n, prop.test),
    tidy_results = map(test_results, broom::tidy)
  ) %>% 
  select(city_state, tidy_results) %>% 
  unnest(tidy_results) %>% 
  select(city_state, estimate, starts_with("conf"))

```

## problem2 

```{r}
data_df = 
  tibble(
  file_name = list.files("./data/zip_data/")) %>% 
  mutate(
    path = str_c("./data/zip_data/", file_name),
    data = map(.x = path, ~read_csv(.x)),
    arm = str_extract(file_name, "[a-z]{1,3}"),
    id = readr::parse_number(file_name)) %>% 
  select(arm, id, data) %>% 
  unnest(data) %>% 
  pivot_longer(
    week_1:week_8,
    names_to = "week",
    values_to = "observations"
  ) %>% 
  mutate(
    week = readr::parse_number(week)
  )
```


```{r}
head(data_df)
```

Make a spaghetti plot showing observations on each subject over time, and comment on differences between groups.
```{r}
data_df %>% 
  unite(arm_id, c(arm, id), sep = " ", remove = FALSE) %>% 
  select(-id) %>% 
  ggplot(aes(x = week, y = observations)) + 
  geom_point(aes(group = arm_id, color = arm)) +
  geom_line(aes(group = arm_id, color = arm))
```

```{r}
##read_file = function(names){
##  file_summary = tibble(
##    names = read_csv("./data/zip_data/file_names")
##  )
##  return(file_summary)
##}
```

```{r}
#file_df = map(file_names, read_file)
```



## problem 3
```{r}
set.seed(10)

iris_with_missing = 
  iris %>%
  map_df(~replace(.x, sample(1:150, 20), NA)) %>%
  mutate(Species = as.character(Species)) %>% 
  janitor::clean_names()
```

write a function. 
```{r}
fill_in_missing = function(x) {
  if (is.numeric(x)) {
    x = replace(x, is.na(x), mean(x, na.rm = TRUE))
  }
  if (is.character(x)) {
    x = replace(x, is.na(x), "virginica")
  }
  return(x)
}
```

```{r}
iris_without_missing =
  map_dfr(iris_with_missing, fill_in_missing)

iris_without_missing

```



